Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-02-17 Report/convergence_centralized.tex
modified convergence

To prove the convergence of the centralized algorithm in \eqref{eqn-6} and \eqref{eqn-mse-1}, we need to show that the following conditions are to be satisfied by the objective function sequence to prove the convergence of the transmit and the receive beamformers.
\begin{itemize}
	\item The objective function should be bounded below
	\item The feasible set should be a compact set
	\item The sequence should be monotonically decreasing for each iteration
	\item Uniqueness of the mapping, \textit{i.e}, there should be one-to-one correspondence between the objective value set and the feasible domain.
\end{itemize}
Assuming the above conditions are satisfied by the iterative algorithm, using Bolzano-Weierstrass theorem \cite{rudin1964principles}, we can show that any bounded monotonically decreasing sequence has a unique limiting point. Using the property of one-to-one mapping between the feasible domain and the objective value, the transmit and the receive beamformers also approaches to a limiting point since the inverse mapping is unique in each iteration. Let us prove the above conditions are satisfied by the centralized problem. Note that the original nonconvex problem in \eqref{eqn-6} and \eqref{eqn-mse-1} has a solution set with the same objective value due to the invariance of the \ac{SINR} expression to the phase rotations, but the relaxed iterative convex problems lead to a unique solution depending on the initialization point.

@@

To prove the boundedness of the objective function, it is enough to show that the objective function is bounded below due to the minimization objective. Since the minimum value of the norm operator is zero, \textit{i.e}, the limiting point is \me{< -\infty}, it is bounded below. Note that the objective function is Lipschitz continuous over the feasible set, and therefore, it is bounded from above as well, since the feasible set is bounded. Note that the objective function is continuous everywhere and not differentiable only at the minimum.

>>>>

To prove the convergence of the centralized algorithm in \eqref{eqn-6} and \eqref{eqn-mse-1}, we need to show that the following conditions are to be satisfied by the objective function sequence to prove the convergence of the transmit and the receive beamformers.
\begin{itemize}
	\item[(a)] The function should be coercive and bounded below
	\item[(b)] The feasible set should be a compact set
	\item[(c)] The sequence should be monotonically decreasing for each iteration
	\item[(d)] Uniqueness of the mapping, \textit{i.e}, there should be one-to-one correspondence between the objective value set and the feasible domain.
\end{itemize}
Using \cite[Prop. A.8]{bertsekas1999nonlinear}, the existence of a global minimizer in the feasible set can be guaranteed if the conditions (a) and (b) are satisfied. Since the feasible set is not fixed in each iteration, we require additional conditions (c) and (d) to prove the global convergence of the objective function, the transmit and the receive precoders. Assuming the above conditions are satisfied by the iterative algorithm, using Bolzano-Weierstrass theorem \cite{rudin1964principles}, we can show that any bounded monotonically decreasing sequence has a unique limiting point. Using the property of one-to-one mapping between the feasible domain and the objective value, the transmit and the receive beamformers also approaches to a limiting point since the inverse mapping is unique in each iteration. Note that the relaxed iterative problem has the unique solution but not the original nonconvex problem. Since the transmit precoders in problem in \eqref{eqn-6} and \eqref{eqn-mse-1} are invariant to any unitary rotations due to the absolute value operator in the \ac{SINR} expression, the limiting point is a set of precoder vectors with different unitary rotations. The limiting point of the iterative algorithm is susceptible to the initial operating point due to the linearization of the nonconvex \ac{DC} constraint.

@@

To prove the boundedness, it is enough to show that the objective function is bounded below due to the minimization objective. Since the minimum value of the norm operator is zero, \textit{i.e}, the limiting point is \me{< -\infty}, it is bounded below. Note that the objective function is Lipschitz continuous over the feasible set, and therefore, it is bounded from above as well, since the feasible set is bounded. Note that the norm operator in the objective function is continuous and coercive over the feasible set but not differentiable at its minimum point. Using the conditions (a) and (b) we can guarantee the existence of a minimizer to the original nonconvex problem in \eqref{eqn-6} and \eqref{eqn-mse-1}.

### 2015-02-17 Report/convergence_distributed.tex
modified convergence

To prove the convergence of the \ac{ADMM} approach, we use the argument presented in \cite{bertsekas1989parallel} Proposition 4.2. 
If the problem is written as 
\begin{IEEEeqnarray}{rCl}
	\underset{\mbf{x},\mbf{z}}{\text{minimize}} &\quad& G(\mbf{x}) + H(\mbf{y}) \eqsub \\
	\text{subject to} &\quad& \mbf{A} \mbf{x} = \mbf{z} \eqsub \label{const-admm} \\
&\quad&	\mbf{x} \in \mc{C}_1, \mbf{z} \in \mc{C}_2, \eqsub
\end{IEEEeqnarray}
following conditions are required for the convergence if \ac{ADMM} is used.
\begin{itemize}
	\item \me{G,H} should be convex
	\item \me{\mc{C}_1,\mc{C}_2} should be a convex set and bounded
	\item \me{\mbf{A}^\herm \mbf{A}} should be invertible.
\end{itemize}
Note that the equality constraint \eqref{const-admm} is identical to \eqref{const-admm1} used in the \ac{ADMM} subproblem \eqref{eqn-dual-3}. It is evident from the equality constraint \eqref{const-admm1} that \me{\mbf{A} = \mbf{I}}, which is an identity matrix and is invertible. The objective function \me{G,H} are \me{\ell_q} norm in \eqref{eqn-decent-1} are convex and the set defined by the constraints of the problem \eqref{eqn-decent-1} are all convex sets and has a nonempty interior. The feasibility of the interior point is verified by having a non zero precoder for only one user. Therefore, by following \cite{bertsekas1989parallel} Proposition 4.2, it can be seen that the \ac{ADMM} approach converges to the centralized solution as \me{i \rightarrow \infty}.

>>>>

To prove the convergence of the \ac{ADMM} approach, we use the argument presented in \cite{bertsekas1989parallel} Proposition 4.2. 
If the problem is written as 
\begin{IEEEeqnarray}{rCl}
	\underset{\mbf{x},\mbf{z}}{\text{minimize}} &\quad& G(\mbf{x}) + H(\mbf{y}) \eqsub \\
	\text{subject to} &\quad& \mbf{A} \mbf{x} = \mbf{z} \eqsub \label{const-admm} \\
&\quad&	\mbf{x} \in \mc{C}_1, \mbf{z} \in \mc{C}_2, \eqsub
\end{IEEEeqnarray}
following conditions are required for the convergence if \ac{ADMM} is used.
\begin{itemize}
	\item \me{G,H} should be convex
	\item \me{\mc{C}_1,\mc{C}_2} should be a convex set and bounded
	\item \me{\mbf{A}^\herm \mbf{A}} should be invertible.
\end{itemize}
Note that the equality constraint \eqref{const-admm} is identical to \eqref{const-admm1} used in the \ac{ADMM} subproblem \eqref{eqn-dual-3}. It is evident from the equality constraint \eqref{const-admm1} that \me{\mbf{A} = \mbf{I}}, which is an identity matrix and is invertible. The objective function \me{G,H} are \me{\ell_q} norm in \eqref{eqn-decent-1} are convex and the set defined by the constraints of the problem \eqref{eqn-decent-1} are all convex sets and has a nonempty interior. The feasibility of the interior point is verified by having a non zero precoder for only one user. Therefore, by following \cite[Prop. 4.2]{bertsekas1989parallel}, it can be seen that the \ac{ADMM} approach converges to the centralized solution as \me{i \rightarrow \infty}.
